---
title: "**DACSS 601 / PS601 - Assignment Two**"
author: "*Mustafa Erdem Kusdil*"
date: "August 10, 2020"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r myData, include=FALSE}

library(tidyverse)


myData <- read.delim("covid-responses.tab", sep= "\t", header = TRUE)



```

## Italy Covid-19 Survey Dataset

Italy Covid-19 Survey(Mar-18) is a dataset collected by the Covid-19 International Behavioral Science Group. This dataset focuses on the Italian public's attitudes,perceptions, and evaluations regarding the COVID-19 crisis. It helps us understand how people in Italy experience the crisis caused by the novel coronavirus. The study also includes data on respondents' socio-demographic aspects and general characteristics.

The dataset includes `r nrow(myData)` observations and  `r ncol(myData)` variables. Each row in this data represents an individual respondent and columns are questions.

A preview of the dataset can be found below:
```{r cols.print=5, rows.print=7, echo=FALSE}
myData
```
